Manuscript_Outputs

### 2024-01-25 Scripts/Stats_Analysis/RMarkdown/ManuscriptOutputs.Rmd
Calibrate using 80% training

# Standardise variables so HR are per sd
data <- data %>% mutate(
  TC_10risk_sd = TC_10risk_cal/sd(TC_10risk_cal),
  gail_10risk_sd = gail_10risk_cal/sd(gail_10risk_cal),
  PRS_bc_sd = PRS_bc_std/sd(PRS_bc_std),
  TEU_BrCa_313_PRS_center = TEU_BrCa_313_PRS_center / sd(TEU_BrCa_313_PRS_center),
  TEU_BrCa_100k_PRS_center = TEU_BrCa_100k_PRS_center / sd(TEU_BrCa_100k_PRS_center)
  )

@@

cal_plot <- function(data, var="TC_10risk", title, xlim=c(0.01,0.07), ylim=c(0.01,0.07)){

@@

  return(plot)

@@

TC_cal <- cal_plot(data=data, var="TC_10risk",
                   title="Tyrer-Cuzick model")
gail_cal <- cal_plot(data=data, var="gail_10risk",
                     title="Gail model") +
  theme(legend.position="none")
TC_cal2 <- cal_plot(data=data, var="TC_10risk_cal",
                   title="Calibrated Tyrer-Cuzick model")
gail_cal2 <- cal_plot(data=data, var="gail_10risk_cal",
                     title="Calibrated Gail model") +
  theme(legend.position="none")

# 2. Save the legend
#+++++++++++++++++++++++
legend <- get_legend(TC_cal)
# 3. Remove the legend from the box plot
#+++++++++++++++++++++++
TC_cal <- TC_cal + theme(legend.position="none")

gridExtra::grid.arrange(TC_cal, gail_cal, legend, TC_cal2, gail_cal2,
                        ncol=3, widths=c(3.5, 3.5, 0.8),
                        top=paste0("Before and after calibration plots of 10-year observed vs predicted risk by predicted risk decile of each model in the whole analysis population (N=", nrow(data), ")"))

>>>>

# Standardise variables so HR are per sd
data <- data %>% mutate(
  TC_10risk_sd = TC_10risk/sd(TC_10risk),
  gail_10risk_sd = gail_10risk/sd(gail_10risk),
  PRS_bc_sd = PRS_bc_std/sd(PRS_bc_std),
  TEU_BrCa_313_PRS_center = TEU_BrCa_313_PRS_center / sd(TEU_BrCa_313_PRS_center),
  TEU_BrCa_100k_PRS_center = TEU_BrCa_100k_PRS_center / sd(TEU_BrCa_100k_PRS_center)
  )

@@

cal_plot <- function(data, var="TC_10risk", title, xlim=c(0, 0.1), ylim=c(0, 0.1)){

@@

  output <- list(plot=plot, cal_slope=cal_slope, cal_intercept=cal_intercept)

  return(output)

@@

TC_train <- cal_plot(data=train_data, var="TC_10risk",
                   title="Tyrer-Cuzick model in training data")
gail_train <- cal_plot(data=train_data, var="gail_10risk",
                     title="Gail model in training data")

TC_test <- cal_plot(data=test_data, var="TC_10risk_cal",
                   title="Calibrated Tyrer-Cuzick model in test data")
gail_test <- cal_plot(data=test_data, var="gail_10risk_cal",
                     title="Calibrated Gail model in test data")

TC_prs_cal <- cal_plot(data=test_data, var="TC_prs_10risk",
                   title="Tyrer-Cuzick model with PRS in test data")
gail_prs_cal <- cal_plot(data=test_data, var="gail_prs_10risk",
                     title="Gail model with PRS in test data")

# 2. Save the legend
#+++++++++++++++++++++++
legend <- get_legend(TC_train$plot)
# 3. Remove the legend
#+++++++++++++++++++++++
gridExtra::grid.arrange(TC_train$plot + theme(legend.position="none"), 
                        gail_train$plot + theme(legend.position="none"), 
                        legend, 
                        TC_test$plot + theme(legend.position="none"), 
                        gail_test$plot + theme(legend.position="none"),
                        NULL,
                        TC_prs_cal$plot + theme(legend.position="none"),
                        gail_prs_cal$plot + theme(legend.position="none"),
                        ncol=3, widths=c(3.5, 3.5, 0.8))
